High quality content reconstruction in images using a high capacity self-embedding algorithm

### 2014-04-07 Paper/main.tex
Added difference expansion description
Added a description for difference expansion as well as a research paper
on it. I have also updated my research .txt file and added another paper
on reversible watermarks that I still need to read

\hspace{0pt} \\
\cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
The method uses these two techniques in combination to achieve a high embedding capacity while keeping distortion relatively low.
The method achieves a PSNR \textgreater 35dB after embedding.
The method achieves an embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.

>>>>

\hspace{0pt} \\
\cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
Difference expansion works by exploiting the high redundancy that are present in images.
With difference expansion the payload is embedded in the difference of pixel values. 
For a pair of pixel values (x,y). \cite {tian2002reversible}
It should however be noted that image quality reduces rapidly as the payload size is increased when using difference expansion. 
The method uses these two techniques in combination to achieve a high embedding capacity while keeping distortion relatively low.
The method achieves a PSNR \textgreater 35dB after embedding.
The method achieves an embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
